---
title: "String Basics Activity"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')



library(tidyverse) 
library(tidyr)
library(forcats)
library(readr)
library(stringr)

```


## Your turn 1

```{r}
set.seed(123)
cell_info <- str_c(
  str_c("Specimen", 1:12),
  sample(c("RNA", "DNA"), 12, replace = TRUE),
  sample(c("H5N1", "SARS5", "COV19"), 12, replace = TRUE),
  sample(seq(as.Date('2022/01/01'), as.Date('2022/06/01'),
             by="day"), 12),
  sep = "_"
)

cell_info
```

### a. Subset the string `cell_info` into a vector that collects strings containing "RNA".

```{r}

```

### b. Subset the string `cell_info` into a vector that collects strings ending with "7".

```{r}

```

### c. Explain what the following code does?

```{r}
str_subset(cell_info, pattern = "Specimen\\d*")
```

### d. Write the code to extract the string "Specimen" with their corresponding number.

```{r}

```


### e. Split all instances of strings in `cell_info` that are separated by "_" to produce both list and matrix.

```{r}
str_split(cell_info, pattern = ___)
```

```{r}
str_split(cell_info, pattern = ____, ____)
```

### f. What does the following chunk of code do?

```{r}
str_remove(cell_info, "^Specimen")
```

### g. Use `str_replace` to achieve the same thing as in part f.

```{r}

```



